Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2019-03-07 Manuscript/manuscript.tex
Additional text from valentine18

>>>>

 Ca2+ primarily binds carboxylates
MD trajectories indicate that Ca2+ primarily binds to the carboxylates. These results are consistent with previous literature (19 , 22 , 32 , 33) but are surprising in the context of the IR results. Previous FTIR results show minimal changes to the carboxylate peaks and large changes to the phosphate and ester peaks (25
). Even though the calcium ions primarily bind with the carboxylates in our MD trajectories, their effect on the electric field around the carboxylates is minimal because of screening by water molecules and averaging of orientations. In contrast, the less polar domain of the carbonyl experiences more significant electric field (Fig. 6). This is consistent with recent 2D IR and ab initio MD simulations by Kuroda and co-workers in which no changes in the IR spectra or relaxation dynamics of the acetate carboxylate were observed in solutions up to 6 M NaCl (69
). Recent results from our own group also point toward larger changes in carboxylate frequencies with a monodentate binding configuration (70). Likewise, in our study, carboxylates are fully hydrated and primarily experience electric field fluctuations from the surrounding water, and the ion does not appear to modify the local dynamics. Calcium ions exert a larger effect on the partially hydrated ester groups at the lipid-water interface, even though the esters rarely bind Ca2+. Further investigation is required to experimentally determine the location of Ca2+ ions.

Ca2+ changes the dynamics and structure of the membrane-water interface
 The ester region remains hydrated
Previous experiments show that Ca2+ impacts the overall hydration of bilayers. Binder et al. found that dried lipid films hydrate differently in the presence of Ca2+ (71
), calorimetric data suggests that PS-Ca2+ binding is driven entropically by both Ca2+ and lipid dehydration (21
), and PS-Ca2+ binding changes the antisymmetric phosphate group’s IR absorption the same way that lipid dehydration does (7
, 26
). PS-rich membranes can even form a separate dehydrated phase, forming cylindrical aggregates, with excessive calcium ions (28
, 44
). The small changes in our measured ester line shapes, both FTIR and 2D IR, indicate that the carboxylate region remains hydrated. In fact, hydrogen-bond populations increase slightly with Ca2+, which points toward a slight increase in hydration.
